In industries such as airlines, steel, and truck rentals, firms have
coordinated to raise prices or reduce capacities using public announcements
such as earnings calls. An enforcement concern is that there are many
undiscovered cases of collusion facilitated by public communications. This
study develops and evaluates a method for finding collusion-facilitating
content in firms' public announcements. We design a large language model
(LLM) to look for such content and then apply it to around 500,000 company
transcripts. The LLM is very selective in that only .06\% of the transcripts
satisfy the criterion for collusive content. The LLM\ is reasonably
effective at rediscovering previously documented episodes and mostly
identifies potential new episodes. A human audit is conducted of the 301
transcripts with the highest LLM\ scores in order to assess its performance
in substituting for human experts. Though there is an uncomfortably high
rate of false positives, the LLM\ identifies many instances of announcements
with collusive content. Its potential is illustrated with a case study
providing evidence of an unlawful agreement in the Brazilian domestic
airline industry. These findings support an an LLM\ being a
critical component of a screening program for competition agencies and
plaintiff law firms. In addition to contributing to the practice of cartel
screening, the paper also advances our understanding of how firms coordinate
through public announcements. As part of the human audit, firms' collusive
content is described and categorized. Messages fall into two broad bins.
First, a firm states that the industry needs to raise prices, reduce supply,
or reduce capacity. Second, a firm expresses how it has been less aggressive
and calls on competitors to join them, either explicitly or implicitly by
saying it is "acting as a leader", commending rival firms who have acted in
a similar manner, or criticizing rival firms that have not.
