Of the \data{audit/sample_count_int} transcripts with the highest
LLM-validated score, the human auditor rated
\data{audit/true_positive_count_int} as containing collusive content and
\data{audit/false_positive_count_int} as lacking collusive content for a
true positive rate of \data{audit/true_positive_rate_pct_percentage1}.
Table~\ref{tab:audit_performance_bins} reports the true positive rate after partitioning the
sample into three roughly equal-sized subsamples (while respecting score
breaks). The true positive rate is decreasing in the score with a true
positive rate of \data{audit/top_bin/true_positive_rate_pct_percentage1} for
the \data{audit/top_bin/count_int} transcripts in the highest bin and
\data{audit/bottom_bin/true_positive_rate_pct_percentage1} for the
\data{audit/bottom_bin/count_int} transcripts in the lowest bin. 

\input{../data/outputs/tables/human_audit_performance_bins.tex}

There are 71 distinct companies in these \data{audit/true_positive_count_int}
true positive transcripts. Table~\ref{tab:si_companies_human_audit} in Online Appendix~\ref{sec:si_companies_human_audit} lists all companies 
along with their primary market. The four companies with the largest number of
transcripts are GOL Linhas A\'{e}reas Inteligentes (7 transcripts) which is a
domestic airline in Brazil, Micron Technology (6) which is a manufacturer
of computer memory and data storage, Norske Skogindustrier (4) which is a
pulp and paper manufacturer, and Coca-Cola Bottlers Japan (4) which was 
mentioned in the Introduction. We will take
a closer look at GOL Linhas A\'{e}reas Inteligentes in our case study.

21 of the \data{audit/true_positive_count_int} transcripts are from
previously documented episodes of companies making public announcements with
collusive content, including 15 associated with the airlines case. 10 of
those 15 airlines transcripts were from companies in the
\textcite{aryal2022coordinated} study: US Airways (3 transcripts), American
Airlines (2), Delta Airlines (2), United Airlines (2), and AirTran (1); and
then there were five transcripts from Air France-KLM (3) and Frontier
Airlines (2). The other previously documented episodes are: broiler
chicken (Pilgrim's Pride), pork (Smithfield Foods, WH Group), and generic
drugs (Teva Pharmaceuticals). In some of these cases -- generic drugs for
sure and possibly broiler chicken and pork -- collusion also involved the
more standard private communications. The LLM flagging them is a reminder
that screening public communications for collusive content could lead to
investigations that uncover the most compelling evidence of illegal
collusion: direct, express, and private communications between competitors.

In the next section, we will analyze the content of the true positives in order to 
better understand how firms are faciliating coordinated conduct. Here, let 
us comment on the false positives to understand how the LLM is getting it 
wrong. Broadly speaking, a transcript was designated as having collusive 
content (and thus being a "true positive") when a company makes reference 
to some form of less aggressive conduct (such as lower capacities and 
higher prices) and connects it to competitors or the industry. In examining 
the 192 false positives, a content analysis finds that 163 of them refer 
to the firm's own conduct or the state of market competition though did 
not connect it to the conduct of competitors or the industry and thereby 
fell short of facilitating coordinated conduct.\footnote{%
Details from the content analysis can be found in Online Appendix~\ref{sec:si_false_positives}.} 67 transcripts 
referred to a firm reducing, restricting, or managing its supply or capacity 
in a manner consistent with higher prices or avoiding lower prices. However, 
it did not say or suggest that this conduct is something the industry should 
or will or needs to do. 48 of the transcripts refer to higher prices - whether 
noting having raised prices or expressing a need to raise prices - or to 
pricing power. Such a statement might be made in the context of reducing 
supply. In 14 transcripts, the firm refers to industry consolidation by 
noting that it has been consolidating, needs to consolidate, or will consolidate. 
In some instances, the firm attributes consolidation to too much supply 
or capacity or too many firms. In sum, while the LLM identified instances 
in which a firm's message was consistent with competing less aggressively,
it did not have the content that encourages similar conduct by 
competitors. The other 29 false positive transcripts lacked any
relevant content in which
case it may be appropriate to classify them as hallucinations. With that
definition, the hallucination rate is 9.6\% (29 out of
\data{audit/sample_count_int}).\footnote{%
Of course, these statements are based on a reading of the excerpts and it is
possible there is more incriminating material elsewhere in the transcript.
However, the LLM was instructed to provide content supporting their
assessment so either they did a poor job with that task or the score is not
justified by the content.}

In concluding, let us note that that a high false positive rate of 64\% is not 
surprising if it 
is rare for a firm to have collusive content in its public announcements. 
Even if the error rate (i.e., the likelihood that a transcript without 
collusive content is given a high score by the LLM) is low, a high fraction 
of transcripts with a high LLM score will not have collusive content when 
sufficently many transcripts lack collusive content. Consistent with this 
hypothesis, the error rate was a very low 0.4\% for the benchmark sample.\footnote{With the audit sample, we are measuring the likelihood that the 
transcript does not have collusive content conditional on it being assigned 
a high score by the LLM. With the benchmark sample, we are measuring the 
likelihood of the LLM assigning a high score conditional on the transcript 
not having collusive content.} Overall, the LLM has performed well in being
able to find many "collusive" needles in the haystack even if there is some hay
in the basket of needles.
