We now measure the performance of the LLMs on the benchmark sample. We are interested both in the LLM's ability to discover collusive communications, and its ability to avoid flagging non-collusive communications as collusive.

We first count how many of the collusive communications in our benchmark human-rated dataset are rediscovered by the LLMs. In our benchmark dataset, we have \data{summary_stats/tagging_performance/human_benchmark_tagged_count_int} collusive communications that human experts rated as collusive. Out of these, \data{summary_stats/tagging_performance/benchmark_collusive_flagged_count_int} (\data{summary_stats/tagging_performance/benchmark_collusive_flagged_pct_percentage0}) were flagged in the large-scale LLM queries, and \data{summary_stats/tagging_performance/benchmark_collusive_validated_count_int} (\data{summary_stats/tagging_performance/benchmark_collusive_validated_pct_percentage0}) were validated as collusive.

While this is far below 100\%, it is also far above zero. This suggests that LLMs are able to discover a significant percentage of collusive communications in a large sample, even if imperfectly.

To understand the rate of false positives, we now count how many of the non-collusive communications in our benchmark dataset were flagged as collusive by the LLMs. In our benchmark dataset, we have \data{summary_stats/tagging_performance/benchmark_not_collusive_count_int} transcripts that human experts rated as not collusive. Out of these, \data{summary_stats/tagging_performance/benchmark_not_collusive_flagged_count_int} (\data{summary_stats/tagging_performance/benchmark_not_collusive_flagged_pct_percentage1}) were flagged in the large-scale LLM queries, and \data{summary_stats/tagging_performance/benchmark_not_collusive_validated_count_int} (\data{summary_stats/tagging_performance/benchmark_not_collusive_validated_pct_percentage1}) was validated as collusive. This is consistent with the standard view that hallucinations happen but are uncommon. Nevertheless, due to the small overall percentage of collusive communications, it suggests that false positives are a significant issue. Even a small rate of hallucinations results in a large percenatge of flagged and validated transcripts being false positives (which we confirm below in the human audit). This suggests that LLMs should be used along with human assistance.

These numbers also show that there is significant signal in the LLM output. We can see this in the stark difference in the rate at which the collusive and non-collusive communications are flagged by the LLM. Transcripts that humans rated as collusive were \data{summary_stats/tagging_performance/benchmark_validation_odds_ratio_int} times more likely to be validated as collusive by the LLM. This suggests that while LLMs are imperfect, they meaningfully distinguish between collusive and non-collusive communications.