This study contributes to addressing two questions: How do firms collude? 
And how do we detect collusion? The focus is on how firms coordinate their 
conduct deploying an underexplored communication practice: public announcements 
such as earnings calls. To address how public communications could 
facilitate collusion, an LLM is deployed to find company transcripts 
with collusive content. The LLM identifies many new episodes which vastly 
adds to the few episodes discovered through public and private enforcement 
\parencite{harrington2022collusion}. A human audit of those episodes reveals some regularities 
in the messages used to coordinate an output or capacity reduction or a 
price increase. Consequently, we are left with a more informed understanding 
of how public announcements can be a cause for anticompetitive concern. 
The human audit is also the basis for addressing the second question as 
it is assesses the performance of the LLM as a screen for collusion. The 
LLM is able to substitute for human experts in finding those rare transcripts 
with collusive content though the rate of false positives means there is 
an essential role for human oversight.

We view our study as an initial step of a research program investigating 
public communications and collusion with the assistance of generative AI. 
Moving forward, let us close with some thoughts on improving the performance 
and how the output of our study can be used for new research projects. 

There is much more that can be done with an LLM.  We have had it evaluate 
each company's transcript in isolation. Having an LLM simultaneously evaluate 
a collection of transcripts could enhance performance. This could be done 
by considering all competitors' transcripts and have it attach a higher score 
when collusive content is more common among competitors. That is a feature 
of the approach taken in \textcite{duso2025public} with a dictionary model. Alternatively, 
an LLM could consider the entire collection of a company's transcripts and have 
it look for changes in the extent of collusive content. While that could be 
performed with the existing model - by looking at scores over time - it may be 
more effective in having an LLM look for the arrival and departure of collusive 
content. A second direction pertains to evaluating performance. The human audit 
examined the transcripts with the highest LLM scores and thus those identified 
as suspicious. While the audit then informed us of the rate of false positives, 
it could not speak to the rate of false negatives; how many episodes is the 
LLM failing to pick up? To do so would mean extending the human audit to some 
of the cases with non-high scores. That may require many more human resources 
but could provide valuable information about an LLM's performance.

Our study has focused on identifying and synthesizing the content of public 
communications that facilitate collusion. A next research step is to explore 
whether it results in effect along the lines of the analyses in \textcite{aryal2022coordinated} 
and \textcite{sheng2024public}. Our analysis has discovered many candidate 
markets for conducting such an empirical analysis. Two necessary elements of 
an episode is that it has a sufficiently rich set of public announcements - in 
particular, variation in the presence of collusive content - and data is 
available on outputs, capacities, or prices so as to measure effect. 

In concluding, we believe an LLM has proven it is street-ready to be 
used by competition agencies and plaintiff law firms to search for episodes 
warranting investigation and possible prosecution or litigation. For that 
purpose, we have proposed a protocol combining the LLM with human oversight. 
It is our hope that this study and that of \textcite{duso2025public} are just the 
beginning of the development of an effective enforcement tool.
