% !TeX root = manuscript.tex
Our transcript text data comes from the Capital IQ transcripts database 
(currently branded as S\&P Global Machine Readable Transcripts). The 
dataset includes earnings calls, investor day presentations, industry 
conferences, analyst meetings, and other public corporate communications.

The transcripts span from \data{summary_stats/dataset_overview/first_date} 
to \data{summary_stats/dataset_overview/last_date}, covering
 \data{summary_stats/dataset_overview/unique_companies_int} companies.
  Our dataset comprises \data{summary_stats/dataset_overview/total_transcripts_int} 
  transcripts. The average call lasts \data{summary_stats/audio_characteristics/mean_length_description}. 
  In total, it would take \data{summary_stats/audio_characteristics/total_audio_years_int} 
  years of uninterrupted audio to listen to all calls. Capital IQ provides 
  verbatim transcriptions of these calls, including remarks by company 
  executives and the subsequent question-and-answer sessions with analysts 
  and investors. Speakers are identified and tracked across the transcripts.

The data includes company identifiers, call dates, and call types. 
We merge Compustat data at the company-year level to obtain basic 
information like sector and market capitalization.

\input{../data/outputs/tables/summary_stats_dataset.tex}

We use expert ratings of collusive and non-collusive transcripts from
 \textcite{aryal2022coordinated}.\footnote{\url{https://doi.org/10.5281/zenodo.5664420}} 
 They collected earnings calls from 11 airlines from 2002 to 2016, a 
 period during which major airlines allegedly tried to enforce ``capacity discipline'' 
 through public communications. They rated the transcripts as collusive
 or non-collusive with a keyword search and manual review. They only 
 coded as collusive the transcripts where all three authors agreed that 
 the transcript was collusive. Their data includes 
 \data{summary_stats/tagging_performance/aryal_total_transcripts_int} 
 transcripts accessed through the LexisNexis database and the investment 
 news website Seeking Alpha, with about \data{summary_stats/tagging_performance/aryal_collusive_rate_pct_percentage0} 
 being coded as collusive. We use \data{summary_stats/tagging_performance/aryal_transcripts_in_ciq_int} 
 of these transcripts that are available in the Capital IQ dataset.
