\subsection{Data Sources for LLM Requests}

Our primary data source consists of transcripts from public corporate communications obtained through S\&P Capital IQ. This dataset encompasses all available public calls, not solely quarterly earnings calls. Coverage includes earnings calls, investor day presentations, industry conferences, analyst meetings, and other public corporate communications.

The transcripts span from \data{summary_stats/dataset_overview/first_date} to \data{summary_stats/dataset_overview/last_date}, covering \data{summary_stats/dataset_overview/unique_companies_int} companies across diverse industries and sectors. Our dataset comprises \data{summary_stats/dataset_overview/total_transcripts_int} transcripts in total. The average call lasts \data{summary_stats/audio_characteristics/mean_length_description}. In total, it would take \data{summary_stats/audio_characteristics/total_audio_years_float} years of uninterrupted audio to listen to all calls. Capital IQ provides verbatim transcriptions of these calls, including both the prepared remarks by company executives and the subsequent question-and-answer sessions with analysts and investors. This broader scope beyond traditional earnings calls is particularly valuable for detecting potential collusive behavior, as discussions of competitive dynamics and capacity decisions may occur in various corporate communication settings.

Each transcript in our dataset includes metadata such as the company identifier, call date, call type, participating executives, and the full text of the discussion. The inclusion of diverse call types strengthens our analysis by capturing a wider range of contexts in which executives might inadvertently signal anti-competitive intentions or discuss market coordination.

\subsection{Extracting Data from Transcripts}

Our approach leverages Large Language Models to systematically identify potential collusive intent in corporate communications at scale. The core challenge lies in replicating the nuanced judgment of human experts who can detect subtle signals of anti-competitive coordination. While human reviewers possess the expertise to identify collusive language in earnings calls, manually reviewing nearly half a million transcripts would be prohibitively resource-intensive. Conversely, automated analysis through LLMs offers computational efficiency but requires carefully crafted prompts that capture the complexity of collusive signaling while producing reliable, interpretable outputs.

We employ zero-shot prompting, where the LLM analyzes each transcript without explicit input-output examples. Initial prompt iterations revealed the importance of specification clarity. A basic prompt such as ``Does the following transcript show evidence of potential collusive intent?'' would prove inadequate for several reasons: it fails to define collusive intent operationally, does not specify how such intent manifests in corporate communications, and lacks guidance on output structure (e.g. binary classification, continuous scale, extracted evidence, etc).

An initial prompt that is still quite simplistic but leads the way for further refinement was: \textit{``Analyze the following earnings call transcript and rate on a scale of 0 to 100 the extent to which the company shows signs of collusive intent. Also provide a brief reasoning for your score.''} Here, beside being more specific about what the response should contain, we make use of an important feature of OpenAI's API, which allows sending such a request along with a defined structure for the response through which we specify what fields the LLM response should contain and what data type (i.e. ``score'' as integer, ``reasoning'' as text string).
% MAYBE include a footnote on why we didn't choose to ask for a binary flag in most prompts

Through iterative refinement, we developed further prompt variants that incorporate insights from the industrial organization literature on tacit collusion. The literature emphasizes that firms may signal coordination through discussions of capacity discipline, pricing intentions, and conditional statements linking their actions to competitor behavior. Following established prompting best practices from both LLM providers and the research community, we decided to structure our prompts to request three key outputs: a collusion intent severity score ranging from 0 to 100, providing a continuous measure of intent strength; a concise reasoning statement explaining the score assignment; and specific excerpts from the transcript supporting the assessment. This multi-faceted output enables both quantitative analysis and qualitative validation of the LLM's determinations. Our goal was to decide on a prompt formulation that not only fits the known type of collusive intent present in our benchmarking sample, but is also general enough that it would result in a useful assessment of the full universe of transcripts.

We compared LLM responses to human assessments as we tried different prompt variants, utilizing two sets of transcripts. The first consists of conference call transcripts from U-Haul, some of which include collusive communications and are discussed in \textcite{harrington2022collusion}. We reviewed the transcripts ourselves and provided collusion severity scores on a 0-100 scale. The other consists of airline industry transcripts flagged by \textcite{aryal2022coordinated} for collusive content. We used their publicly available binary assessment of collusion. To make these two benchmarking sets comparable, we also produced a binary classification for the U-Haul sample using a threshold value that we ultimately set to 50. Qualitative review of discrepancies between LLM and human assessments informed further prompt adjustments, particularly in cases where the model either over-detected language about competition as collusive or under-detected subtle coordination signals. Concomitantly, we focused on the ``reasoning'' from the LLM responses in an attempt to understand how the justification for different ``score'' levels changes. 

% TBD if the following paragraph is good.
% Also, we should decide if we want to make all relevant prompts available in an appendix, or simply state that they can be found in the replication package.
In sum, the differences between prompt variants came from the way we indicated a company can signal their willingness or desire to coordinate. Our decision on what to edit in the prompt text was based on how well we could use the LLM output to distinguish where collusive intent was identified or not in the expert benchmark set. While there are many different measures available to assess the performance of a prompt based on its output, in trying to avoid identifying cases of true collusive intent, we generally preferred prompt variants that produced few false negatives and also where the LLM scores matched the scores on the U-Haul benchmarking subsample more closely (since we didn't have a score for the airlines subsample). 
%MAYBE do we want to say that we recognize this prompt selection can be done better in the future, or do we want to leave that to the conclusion section where we point to possible future work?

Our final prompt version instructs:
\begin{quote}
\textit{You’re an expert in detecting subtle collusive intent in company earnings calls. You know firms can try to avoid scrutiny if they express intentions to reduce supply or increase prices, or they can imply it would be good if industry capacity were limited or prices were kept high. Analyze the following transcript of a public company communication and identify any signs that the company is trying to coordinate with competitors to limit capacity or keep prices high. Provide a score from 0 to 100, where 0 means no evidence of collusive intent and 100 means strong evidence of collusive intent. Additionally, provide a very brief explanation of your assessment. Also provide a list of excerpts that support your assessment.}
\end{quote}

This prompt was crafted to mention the broad types of collusive actions (i.e. maintaining high prices, limiting capacity), specify clearly that we target a company's intention to coordinate on such actions, and indicated exactly the appropriate response format, keeping the full prompt text concise. Particularly for this prompt, we initially assessed the output based on a version that was identical to the above except that it didn't include the request for excerpts. We eventually decided that when we deploy the LLM request on the full sample of available transcripts, we should include the request for excerpts so we can allow further manual inspection of LLM response quality.

With the prompt finalized, we processed the complete corpus of transcripts through OpenAI's API using their batch processing infrastructure. This approach enabled efficient parallel processing while respecting API rate limits. The processing took several days, but could run continuously in the background without manual intervention. Still, due to API usage rate limits, we had to implement a system that forced pauses in our submissions when our available processing queue at OpenAI was almost full, to allow part of the pending batches to complete before resuming. Once the processing finished, we had the LLM response strings stored in a large database, structured such that we could easily clean them up and extract the score, reasoning and set of excerpts for analysis.

Throughout the process of refining the prompt, we use LLM versions as released by OpenAI (primarily 
\textit{gpt-4o-mini} as it was the fastest and cheapest of the most advanced models at the time of our analysis), so we do not train a model specifically for the task at hand. However, OpenAI do provide options to request and pay for a fine-tuned version of one of their models, either based on a sample of input-output pairs, or on a set of more/less preferred output versions for every given input provided in the training sample. The goal of choosing either option is to get the general-purpose LLM to produce output that is hopefully more relevant and precise to a specific goal, but is not guaranteed to do so. Moreover, OpenAI recognize in their related documentation that for data extraction tasks, extensive prompt engineering is the first step to pursue (i.e. manually refining prompt formulation), and only upon seeing no improvement does it become potentially helpful to opt for fine-tuning services. They also suggest that users should expect only modest performance improvements from fine-tuning, depending on their exact task.
% MAYBE include a source for this documentation
