% !TeX root = manuscript.tex
It is well documented that firms use
public communications to collude. Private litigation has delivered
compelling evidence of communications through earnings calls and semi-public
industry meetings which resulted in firms jointly reducing their capacities
in the airlines and steel industries.\footnote{%
All of the cases referenced in this and the ensuing paragraph (with the
exception of the EU tire manufacturers case) can be found in
\textcite{harrington2022collusion}.} Plaintiffs have documented
public communications to
facilitate coordination in the chicken and pork processing industries as
well as to supplement private communications for a generic pharmaceuticals
cartel.

These public announcements can be egregious. For example, a 
Delta Airlines vice president explicitly called for airlines to
coordinate capacity reductions in an earnings call:

\begin{quotation}
\noindent I think Delta can't do it alone. We have to do it in conjunction with the
other carriers because certainly the capacity cuts that we can do on our
own, while they will help us, will not remedy the industry's woes. \ldots{}
And I would say if the industry could achieve a 10\% reduction in capacity
year-over-year by the fall that we'd be in pretty shape \ldots{} \footnote{%
Delta Air Lines, Inc., Q1 2008 Earnings Conference Call (April 23, 2008).
Cited in \textcite{harrington2022collusion}, p. 549.}
\end{quotation}

\noindent This announcement was one of many made by several airlines calling
for ``capacity discipline'' and commending the industry when it was achieved.
The empirical analysis of \textcite{aryal2022coordinated} showed that these
announcements did cause significant capacity reductions.

There have also been some cases pursued by competition agencies. Under
\S~5 of the Federal Trade Commission Act, the Federal Trade Commission
issued consent decrees prohibiting certain public communications in the
markets for print advertising and one-way truck rentals. The Dutch
competition authority obtained a commitment against mobile telecom
operators that prohibited them from making certain public announcements
relating to their pricing. Most recently, the European Commission has a
case against tire manufacturers in which ``at the heart of the
investigation is the novel claim that the tiremakers may have used `public
communications,' in particular earnings calls, as part of a strategy to
collude over prices.''\footnote{%
Nicholas Hirst and Jean Comte, ``Michelin tells court there's `no evidence'
underpinning EU cartel raids,'' MLex, March 5, 2025.} While there have been
few prosecutions under \S~1 of the Sherman Act by the U.S. Department of
Justice's Antitrust Division, it is not because such cases cannot
succeed.\footnote{%
To our knowledge, the last case was more than thirty years ago. It
involved advance price announcements in the airlines industry (\textcite{borenstein2004rapid}) rather than
announcements referencing rival firms' conduct. That case was less egregious than the aforementioned airlines
``capacity discipline'' episode.} Courts have recognized that ``collusive
communications can be based upon circumstantial evidence and can occur in
speeches at industry conferences, announcements of future prices,
statements on earnings calls, and in other public ways.''\footnote{\textit{In re Delta/AirTran Baggage Fee
Antitrust Litig}., 733 F. Supp. 2d 1348, 1360 (N.D. Ga. 2010).}

This study has two objectives. First, to advance our understanding of collusion through public communications. 
This type of collusive practice has only recently been the subject of analysis and, consequently, little is known about it. 
Second, improve enforcement. There is the concern that the 
few cases thus far pursued by public and private enforcers may be only the tip of the iceberg. 

To do so, we employ natural language processing using a large language model (LLM) to detect collusive content.
We define "collusive content" 
as content that facilitates coordinated conduct among competitors to reduce competition. 
Across NLP benchmarks, modern LLMs substantially outperform traditional methods on nuanced understanding tasks (\textcite{brown2020language}; \textcite{openai2023gpt4}).

Using the LLM, we discover many previously unidentified company transcripts containing collusive content. With those 
transcripts, we organize the associated collusive content to better understand how it could 
affect competition. While we do not explore the effect of this communication on prices or quantities, our study 
produces a set of candidate markets for conducting such an empirical analysis. 
We hope researchers will exploit it. Turning to the enforcement objective, we show how the LLM can be used by 
competition agencies and plaintiff law firms to identify possible cases to prosecute or litigate.  
The analysis of the content used in such communications provides the basis for writing guidelines to instruct 
firms what they should not be saying and what content may be the basis for an investigation.

Achieving these objectives requires discovering communications with collusive content. When collusion involves private 
communications, the challenge is that firms do their best to keep those communications secret. When it 
involves public communications, the challenge is quite different. Accessibility is not a problem as the 
communications are in the public domain. The challenge is instead akin to finding a "needle in a haystack." 
There is a massive volume of public communications produced by thousands of companies and reviewing it all 
in search of possible collusive content would seem a fool's errand.

We discuss practical issues and limitations of the approach. The first step is to properly design a prompt. Guided 
by some previously documented cases of collusion with public announcements, we experimented 
with prompts and refined them to find one effective at flagging transcripts with collusive content. A scoring 
process was then constructed by which the LLM assigns a score to each transcript. With the prompt 
and scoring process in place, \data{summary_stats/dataset_overview/total_transcripts_int} transcripts were run through the LLM to look for collusive 
content. Those transcripts with the highest scores were then reviewed by a human expert. The human audit 
is integral to both research objectives. First, the audit distills and organizes the content to 
understand the collusive messages being conveyed by firms. Second, the audit evaluates the LLM's performance 
and thus assesses its potential as a screening tool for enforcers.

Prior to describing how the LLM contributes to those two objectives, let us first summarize its output. 
To begin, the LLM is very selective as it filters out \data{summary_stats/tagging_performance/llm_filter_out_rate_pct_percentage2} of all transcripts which is consistent 
with our prior belief that collusive content is rare (though common enough to be an antitrust concern). 
Critically, the LLM is able to systematically discover companies' announcements with collusive content. 
In some instances, it rediscovers previously documented communications such as the aforementioned 
airlines episode. Thus, the LLM was able to find these few collusive "needles" amidst hundreds of 
thousands of noncollusive "hay."  

A concern is that the LLM has been trained on a corpus which includes
references to documented cartel episodes, such as those in
\textcite{aryal2022coordinated} and \textcite{harrington2022collusion} or
newspaper stories and legal briefs. In that case, it is only reciting what
it learned from ``reading.'' Assuaging that concern, we find that most of
the collusive messages found pertain to new episodes. Here are two
illustrative examples.

\begin{itemize}
\item Kirby Corporation is a leading tank barge operator which transports
bulk liquid products in the U.S. river and coastal systems. In its Q4 2017
earnings call, CEO David Grzebinski called on competitors to follow its
lead in reducing industry capacity: ``We have done our part to rationalize
the industry's fleet and improve our profitability going forward, but we
need the industry to mirror our actions. If others will follow our lead, an
accelerated balance can be restored to the struggling market.'' He
then went on to state how much industry capacity needed to be cut: ``I
would say 1.5 million to 2 million barrels of capacity needs to come out. We
did ... 830,000 barrels ... So if others do their part we could get back in
the balance a lot sooner ...''

\item During a series of earnings calls, Coca Cola Bottlers Japan conveyed
its role as price leader in the beverage market and how raising prices will
promote industry profitability. In an earnings call in February 2023,
President Calin Dragan stated: ``I'm very pleased to see that the entire
industry moved to action and acted responsibly last year. So we were able,
for the first time, to put the prices up and that's a great thing for our
business and for our industry.'' He went on to say: ``This price increase
should not be just onetime event ... That's a recipe for failure, not for
our business, but for industry. So this, in my opinion, should become a
norm in our business here in Japan ...'' Later that year, during the Q3
2023 earnings call, executive Costel Mandrea conveyed: ``We took leadership
in making price decisions in Japanese market, and we will do whatever is
needed in order to continue increasing profitability, but also making sure
we have a healthy beverage industry in Japan.'' This point was underscored
by President Dragan: ``Throughout the years, we were leading in price
increases implementation, and in the future, we are not going to be the one
which is going to drag back the industry into this because we believe that
this is a healthy instrument for the health of the industry.''
\end{itemize}

\noindent The LLM was able to discover these messages along with many other
transcripts containing collusive content.

The human audit reviews the \data{summary_stats/tagging_performance/human_audit_sample_count_int} company transcripts assigned the
highest score by the LLM. While there is a rich variety of collusive content,
more than 90\% of the transcripts can be placed into one of five categories:

\begin{enumerate}
\item A firm announces the industry has reduced supply or capacity and references competitors
or the industry in a manner supportive of such conduct.

\item A firm announces the industry needs to reduce supply or capacity or to show discipline.

\item A firm announces the industry has shown or will show supply or capacity or price
discipline.

\item A firm announces the industry needs to raise prices.

\item A firm announces it is being or will be less aggressive in pricing and references
competitors' conduct in a manner encouraging similar conduct.
\end{enumerate}

This synthesis of the content informs us of the manner in which public announcements facilitate coordinated conduct.
Coordination is an understudied area compared to research on how firms design the collusive
agreement (i.e., collusive strategies) and achieve cartel stability (i.e.,
satisfy equilibrium conditions).\footnote{%
In the language of game theory, research is almost entirely focused on
understanding the collusive equilibrium upon which firms settle.
Coordination is about how firms move from a competitive (static Nash)
equilibrium to a collusive (repeated game) equilibrium.} Especially when the
method of coordination does not involve direct, express, and private
communication (i.e., the proverbial \textquotedblleft
smoke-filled\textquotedblright\ room), it is important to understand how
firms communicate as that can affect the form collusion takes (e.g., firms
may raise prices but without a market allocation scheme) as well as the
likelihood of collusion (e.g., whether firms achieve mutual understanding to
raise prices).\footnote{%
Our study focuses on a particular class of public announcements. Other less
explicit coordinating practices include advance price announcements
(\textcite{borenstein2004rapid}, \textcite{chen2017preannouncements}), coded
messages (\textcite{cramton2000collusive}, \textcite{harrington2025nonexpress}),
and price signaling (\textcite{byrne2019learning}, \textcite{byrne2025platforms}).}

The study's second objective is to contribute to enforcement by developing a 
screening tool for collusion involving public communications. The LLM's 
ability to identify a diverse array of collusive content is impressive. At 
the same time, the false positive rate is 64\% (where a false positive means 
the LLM says there is collusive content but the human expert disagrees). 
However, if only a small percentage of company transcripts genuinely have 
collusive content - which seems reasonable - then even a low error rate will 
produce many false positives. Thus, a high false positive rate may 
be inevitable. What is crucial for enforcement is that the LLM identifies 
collusive content that can be the basis for an investigation. Our takeaway is that 
an LLM, when complemented with human oversight, can be part of an effective 
screening program. To show proof of concept, we provide a case study of the 
Brazilian domestic airline industry. The LLM identifies suspicious content 
and subsequent examination reveals convincing evidence of two airlines 
effectively communicating to coordinate a reduction in their capacities.

This second contribution adds to the growing literature on 
cartel screening. Generally, screening involves looking for collusion
in data sets comprising prices or bids (in the context of a procurement
auction). This could mean testing for collusive markers (i.e., patterns more
consistent with collusion than competition) or for structural breaks
associated with cartel birth or death.\footnote{%
\textcite{harrington2008detecting}, \textcite{harringtonimhof2022cartel}, and
\textcite{oecd2024detecting} offer surveys of cartel screening. For some
recent research, see \textcite{huberimhof2019machine},
\textcite{kawai2022detecting}, \textcite{chassang2022robust},
\textcite{kawai2023bidrotation}, \textcite{silveira2023who}, and
\textcite{aaltio2025complementary}.} In contrast, our method works on text
rather than numerical data and fits into a body of work on ``text as data''
(\textcite{gentzkow2019text}).

\medskip

\textbf{Literature Review }

Most relevant to our study is the recent literature on the use of public
disclosures to facilitate collusion. Exploring the choice of firms to
collude through private or public communications, \textcite{bourveau2020corporate}
find that as cartel enforcement against explicit collusion
increases - as measured by the rise in leniency programs - firms reveal more
proprietary information through financial disclosures including earnings
calls. They argue that this information sharing is conducive to tacit collusion.
 \textcite{kepler2021private} also looks at the trade-off between public
and private information sharing in the context of firms' coordinating prices
or outputs. He finds that when firms form strategic alliances - which gives
them the opportunity to privately exchange information - firms disclose less
about their expected future business conditions and production decisions in
their public announcements. \textcite{pawliczek2022facilitating} test
whether firms having stronger incentives to collude - and thereby are more
likely to be trying to collude - results in more public disclosures. The
source of variation in the proclivity to collude is the degree of common
ownership across firms. As common ownership increases, firms disclose more
about business conditions and strategies in their earnings calls.

The next three studies more directly examine the relationship between public
announcements and collusive conduct. \textcite{harrington2022collusion} collects and
categorizes all known cases in which there is evidence that firms
coordinated using public announcements which reference rival firms. A
typology of announcements is created which is reviewed in Section~\ref{sec:content}. \textcite{aryal2022coordinated}
and \textcite{sheng2024public} measure the effect of public
announcements on firms' conduct. For the airlines industry, \textcite{aryal2022coordinated}
find that when all airlines on a route have "capacity discipline" or
related content in their earnings calls then their capacities (as measured
by seats) decline by around 2\% in the ensuing quarter. This decrease is
more than half of the average inter-quarter variation. For the broiler chicken industry, \textcite{sheng2024public}
examine the effect on various output measures of the frequency of firms using the words "cut,
balance, constrain, discipline, reduction, or adjustment" in their earning
calls. A 1\% increase in their frequency is
associated with a 1-1.5\% decrease in output depending on the measure.

The preceding three studies focused on previously documented cases of
collusion. Our study's objectives require finding new episodes in which 
public announcements facilitate coordinated conduct. The most 
closely related study is
\textcite{duso2025public} which is the first to apply
Natural Language Processing to a large corpus of company public
announcements in search of collusion. Rather than use an LLM, they use a
dictionary approach as in \textcite{aryal2022coordinated} and \textcite{sheng2024public}.
Bigrams - or pairs of words - are defined to capture a firm referring to its
strategy or to its competitors; e.g. "competitor should" and "raise price".
The score for a firm in a quarter is the number of times those bigrams
appear in its public announcements for that quarter. The study provides
examples showing how this screening approach can identify public
announcements with collusive content. Our study differs in terms of methods 
and objectives and, more specifically, the use of an LLM and the conducting 
of a human audit. The human audit allows us to evaluate the performance of 
our LLM-based screen and to advance our 
understanding of the content used by firms to coordinate in reducing competition. 
\medskip

\textbf{Roadmap }

The data used in our analysis along with the development process for the LLM 
screen are described in Section~\ref{sec:data}. The output from the large-scale LLM analysis 
is summarized in Section~\ref{sec:basic}. In Section~\ref{sec:audit}, the procedure for the human audit is 
described and the performance of the LLM is evaluated. The content identified 
by the LLM is distilled and organized in Section~\ref{sec:content}. Section~\ref{sec:detection} discusses the role of an LLM in a screening 
protocol. Finally, a case study of the Brazilian domestic airline industry 
is provided in Section~\ref{sec:case}.