To systematically evaluate our approach, we benchmark the performance of our main prompt (SimpleCapacityV8.1.1) against three sets of human-evaluated transcripts. First, we use the benchmark dataset described in the methodology section, which combines U-Haul transcripts from \textcite{harrington2022collusion} (scored manually by us on a 0-100 scale, with \data{benchmarking/test_set/joe_rated_int} transcripts) and airline industry transcripts from \textcite{aryal2022coordinated} (with \data{benchmarking/test_set/acl_rated_int} binary collusion flags). These benchmark samples have a high concentration of collusive communications and serve as our primary test set. Additionally, we evaluate performance on \data{benchmarking/test_set/human_audit_int} transcripts from our human audit of the highest-scoring LLM outputs, providing insight into real-world false positive rates.

Table \ref{tab:benchmarking} presents our benchmarking results in two panels. Panel A compares three different approaches for identifying collusive communication using gpt-4o-mini: (1) LLM Flagged, which uses a single query with score $\geq$ 75; (2) LLM Validation, which averages up to 11 repeated queries for initially flagged transcripts; and (3) LLM with Follow-up Analysis, which adds excerpt validation in an attempt to reduce false positives. Panel B shows the performance of different models using the LLM Flagged approach.

First, the results show that the simplest approach (LLM Flagged) performs best on the test set with an F1 score of \data{benchmarking/approach_comparison/llm_flagged_f1_float} on the combined test set. The validation steps, designed to reduce false positives, actually hurt overall performance: LLM Validation achieves an F1 of \data{benchmarking/approach_comparison/llm_validation_f1_float}, and adding follow-up analysis further reduces it to \data{benchmarking/approach_comparison/llm_with_followup_f1_float}. This suggests that while these additional steps may reduce false positives, they also eliminate many true positives.

Second, there is substantial variation in model performance. The best performing model is \data{benchmarking/best_performance/model}, achieving an F1 score of \data{benchmarking/best_performance/f1_score_float} on the combined test set. Notably, the newer models (gpt-4.1-nano, gpt-4.1-mini, o4-mini) fail to detect collusive communication effectively, with F1 scores near zero, suggesting they are not suitable for this task.

\begin{table}[ht]
    \centering
    \caption{Benchmarking Results}
    \label{tab:benchmarking}
    \input{../data/outputs/tables/benchmarking_combined.tex}
    \begin{minipage}{\textwidth}
        \vspace{1em}
        \footnotesize
        \textit{Notes:} F1 scores for different approaches and models on human-rated test sets. Joe's ratings use a threshold of 50 to convert continuous scores to binary labels. ACL's ratings are already binary. The combined set uses ACL labels when available, otherwise Joe's binary labels. Audit F1 shows performance on the \data{benchmarking/test_set/human_audit_int} human-audited top-scoring transcripts. Panel B lacks audit scores because human audits were only conducted on transcripts from our main production run using gpt-4o-mini; other models were tested solely on the benchmark dataset.
    \end{minipage}
\end{table}

The human audit of top-scoring transcripts provides additional insight into false positive rates. Among the \data{benchmarking/test_set/human_audit_int} audited transcripts, \data{benchmarking/test_set/human_audit_true_int} were confirmed as truly collusive, while \data{benchmarking/test_set/human_audit_false_int} were false positives. The LLM Flagged approach achieves a precision of \data{benchmarking/human_audit_performance/flagged_precision_float} on this sample. The follow-up analysis improves precision to \data{benchmarking/human_audit_performance/with_followup_precision_float} by removing \data{benchmarking/human_audit_performance/false_positives_removed_int} false positives, though recall drops to \data{benchmarking/human_audit_performance/with_followup_recall_float}.

These benchmarking results highlight both the promise and limitations of using LLMs for detecting collusive communication. The trade-offs between precision and recall across different approaches suggest that the optimal configuration depends on the specific use case—whether false positives or false negatives are more costly. The discrepancy between performance on matching the different human ratings also reveals the subjective nature of identifying collusive communication, with the model achieving better alignment with ACL's more structured binary assessments.